Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-12 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

Given a random variable~$X$ and a probability measure~$\pmeas$,
the expectation value of $X$ is 
\begin{eqnarray*}
\int X\rmd\pmeas & = & \sum_{i=1}^{N}x_{i}\pmeas\left(A_{i}\right)\textrm{ .}
\end{eqnarray*}
Intuitively, the expectation value is weighted average of the possible
outcomes of $X$ with the weight equal to the probability of each
outcome could happen. For example, consider the random variable~$X_{0}$
representing the number of tails. For the probability measure~$\pmeas$
in example~\ref{ex1}, the expectation value of $X_{0}$ is
\begin{eqnarray*}
\int X_{0}\rmd\pmeas & = & 0\cdot\pmeas(\{HH\})+1\cdot\pmeas(\{HT,TH\})+2\cdot\pmeas(\{TT\})\\
 & = & 0\cdot\frac{1}{3}+1\cdot\frac{2}{3}+2\cdot0=\frac{2}{3}\textrm{ .}
\end{eqnarray*}

After we discussed the conventional expectation value, we can start
to discuss the expectation value of IVPM. First, the only source use
the exact same definition as ours is written by Jamison and Lodwick~\cite{JamisonLodwick2004}
so it's reasonable to start from their definition of integration\footnote{Although they said they would explore their integration in more details,
they change their definition of IVPM later. Hence, I don't know if
they have any further development of their integration.}. Their integral of $X$ is defined by 
\begin{eqnarray*}
\int_{A}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)},\right.\\
 &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)}\right]\textrm{ .}
\end{eqnarray*}
In this definition, we still work on the weighted average. Since we
don't know the exact probability, we want to average on all possible
allowed probability, which represents the requirement on $a_{i}\in\bar{\mu}\left(A_{i}\right)$.
However, I don't have a clear intuition on why they want $\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)$
and $\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)$, and we will
have a more intuitive definition following this line when we move
on to Choquet integral.

>>>>

Given a random variable~$X$ and a probability measure~$\pmeas$,
the expectation value of $X$ is 
\begin{eqnarray}
\int X\rmd\pmeas & = & \sum_{i=1}^{N}x_{i}\pmeas\left(A_{i}\right)\textrm{ .}
\end{eqnarray}
Intuitively, the expectation value is weighted average of the possible
outcomes of $X$ with the weight equal to the probability of each
outcome could happen. For example, consider the random variable~$X_{0}$
representing the number of tails. For the probability measure~$\pmeas$
in example~\ref{ex1}, the expectation value of $X_{0}$ is
\begin{eqnarray*}
\int X_{0}\rmd\pmeas & = & 0\cdot\pmeas(\{HH\})+1\cdot\pmeas(\{HT,TH\})+2\cdot\pmeas(\{TT\})\\
 & = & 0\cdot\frac{1}{3}+1\cdot\frac{2}{3}+2\cdot0=\frac{2}{3}\textrm{ .}
\end{eqnarray*}

After we discussed the conventional expectation value, we can start
to discuss the expectation value of IVPM. First, the only source use
the exact same definition as ours is written by Jamison and Lodwick~\cite{JamisonLodwick2004}
so it's reasonable to start from their definition of integration\footnote{Although they said they would explore their integration in more details,
they change their definition of IVPM later. Hence, I don't know if
they have any further development of their integration.}. Their integral of $X$ is defined by 
\begin{eqnarray*}
\int_{A}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)},\right.\\
 &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)}\right]\textrm{ .}
\end{eqnarray*}
In this definition, we still work on the weighted average. Since we
don't know the exact probability, we want to average on all possible
allowed probability, which is represented by the requirement on $a_{i}\in\bar{\mu}\left(A_{i}\right)$.
However, I don't have a clear intuition on why they want $\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)$
and $\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)$, and we will
have a more intuitive definition following this line when we move
on to Choquet integral~\cite{Choquet1954,Grabisch2016}.
